---
title: "p8105_hw5_nja2140"
Author: Naina Ahuja
Assignment: Homework 5
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
  )

set.seed(10)
```
Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.

```{r}
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```
```{r}
fn_one = function(x){
  if(is.numeric(x) == TRUE){
    x = x %>% replace_na(mean(x, na.rm = TRUE))
  }
  if(is.character(x) == TRUE){
    x = x %>% replace_na("virginica")
  }
  
  return(x)
}

iris_with_missing = map_df(iris_with_missing, fn_one)
```
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary




